---
title       : Predicting Species on Iris Data Set
subtitle    : Classification Trees
author      : Mani Khanuja
job         : Data Scientist
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Objective

* Create a shiny app to perform predicitive analysis. 
* Identify the species based on Sepal & Petal characteristics
* Algorithm used: Classification Trees
* User enters the length & width of Petal & sepal and alogrithm predicts the species based on the Iris data set. 

--- .class #id 

## Accuracy of Classification Trees Algorithm on Iris Data

```{r include=FALSE, results='hide'}
# Load Required Libraries
library(caret)
library(dplyr)
library(AppliedPredictiveModeling)
library(ggplot2)
library(rattle)
#Set Seed and Load Data
set.seed(3433)
data(iris)
#Partition Data
inTrain = createDataPartition(iris$Species, p = 3/4, list = FALSE)
training = iris[ inTrain,]
testing = iris[-inTrain,]
```

```{r}
modFit <- train(Species ~., method = "rpart", data = training)
modFit$results
```

---

## Prediction Example

```{r}
predictfinal <- predict(modFit, testing, type="raw")
predictfinal
```

---
## More Information

* All documents and resources are present in the [github repository](https://github.com/manikhanuja/Data_Products)

#### Thank You!
